### 2011-07-16 doc/theses/svirec/kap4.tex
added implementation chapter

\chapter{Proposed Algorithm}

@@

To represent an XML document we use an extended R-XML tree (Definition \ref{rxmlTree}), called RW-XML tree, which has weights assigned to each node of the tree. The weight of an node is from interval $[0,1]$ and indicates correctness of the data the particular node holds, that means the higher the weight is, more correct particular node is. The weights are used to measure cost of repair candidates, where candidate with the lowest cost is picked to be applied to the XML tree. This is also a first place where interaction of the user can be applied. The user could assign weights to the nodes manually (described in \todo{sem doplnit odkaz do implementacnej sekcie}) or can use some sort of statistical methods to generate them automatically. If the user not assign weights nor use statistical methods, default weight is assigned to all nodes. A definition of an RW-XML tree follows:

>>>>

\chapter{Proposed Algorithm}\label{kap4}

@@

To represent an XML document we use an extended R-XML tree (Definition \ref{rxmlTree}), called RW-XML tree, which has weights assigned to each node of the tree. The weight of an node is from interval $[0,1]$ and indicates correctness of the data the particular node holds, that means the higher the weight is, more correct particular node is. The weights are used to measure cost of repair candidates, where candidate with the lowest cost is picked to be applied to the XML tree. This is also a first place where interaction of the user can be applied. The user could assign weights to the nodes manually or can use some sort of statistical methods to generate them automatically. If the user not assign weights nor use statistical methods, default weight is assigned to all nodes. A definition of an RW-XML tree follows:
